\documentclass[../thesis.tex]{subfiles}

\begin{document}

\chapter*{Dissemination}
\addcontentsline{toc}{chapter}{Dissemination}
\subsection*{Publications}
\begin{itemize}
    \item A survey of OR/MS models on care planning for frail and elderly patients. E. Williams, D. Gartner, P. Harper. Operations Research for Health Care, 2021 \cite{Williams2021}
\end{itemize}



\subsection*{Presentations}
\begin{itemize}
    \item Multi-site and Multi-service Modelling for Elderly and Frail Patients (Poster). ORAHS, Online via Video Conferencing, July 2020
    \item Multi-site and Multi-service Modelling for Elderly and Frail Patients (Poster). 3$^{rd}$ IMA and OR Society Conference, Online via Video Conferencing, April 2021.
    \item Multi-site and Multi-service Modelling for Elderly and Frail Patients (Poster). SIAM Student Chapter National Conference, Online via Video Conferencing, April 2021.
    \item Multi-site and Multi-service Modelling for Elderly and Frail Patients, INFORMS Healthcare, Online via Video Conferencing. July 2021
    \item Predictive Analytics Applied to Hospital Services for Elderly and Frail Patients, University of South Wales Seminar Series, Online via Video Conferencing, January 2022.
    \item Using Predictive and Prescriptive Analytics Within Hospital Services for Elderly and Frail Patients. Welsh Mathematics Colloquium, Gregynog (Wales), May 2022.
    \item Linking Predictive and Prescriptive Analytics for Healthcare Services: The Case of Frail and Elderly Patients. CORS/INFORMS International Conference, Vancouver (Canada), June 2022.
    \item Linking Predictive and Prescriptive Analytics for Healthcare Services: The Case of Frail and Elderly Patients. ICHI IEEE Doctoral Consortium, Rochester, Minnesota (USA), June 2022
    \item Linking Predictive and Prescriptive Analytics for Healthcare Services: The Case of Frail and Elderly Patients. OR64,Warwick (UK), September 2022 
\end{itemize}
\vfill

\end{document}
